Analysis of split plot design using MCMCglmm

### 2017-08-25 README.Rmd
Update README.md
Remove link in "Data"

**Text and figures:**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code:** See the [DESCRIPTION](DESCRIPTION) file

**Data:** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

>>>>

Text and figures:  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

Code: See the [DESCRIPTION](DESCRIPTION) file

Data: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
